Thermodynamic fragments in magic state theories

### 2021-01-12 magic_paper.tex
Thermal Wigner for H=(1,0,0)

>>>>

Take the simplest scenario, where Hamiltonian $H$ has spectrum $(1,0,0)$.
Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
    \hline
    $(0,0)$ & $-\frac{1}{3}$ & $\frac{1}{3(1+2e^\beta)}$ & $-\frac{1}{1+2e^\beta}$ \\
    \hline
    \makecell{$(0,1)$ \\ $(0,2)$} & $\frac{1}{6}$ & $\frac{1}{3(1+2e^\beta)}$ & $\frac{1}{2(1+2e^\beta)}$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,2)$} & $\frac{1}{6}$ & $\frac{1}{3(2+e^{-\beta})}$ & $\frac{1}{2(2+e^{-\beta})}$
  \end{tabular}
  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$.
  The order of the ratio depends on temperature $\beta$ with a threshold value of $\beta_{\rm{thr}} \approx 0.48$.}
  \label{tab:thermal_w}
\end{table}
To construct the Lorenz curves, we need to sort the ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$, but sorting depends on temperature $\beta$.
